### 2008-07-29 doc/storage_system/arc1-storage-documentation.tex
small changes based on the last comments of Aleksandr

We have a file on our local disk we want to upload to a collection called \verb#/ourvo/common/docs#. (See Figure~\ref{fig:uploading}.)
\begin{enumerate}
\item We contact a Bartender to put the file, we give the size and checksum and other metadata, and the transfer protocols we want to use. And of course we give the Logical Name we want to be the name of the file, which in this case will be \verb#/ourvo/common/docs/proposal.pdf#
\item The Bartender ask a Librarian to traverse this LN.
\item If the Librarian can traverse the whole LN then this LN is already exists, but if the LN is still available and the parent exists, the Librarian’s response contains the GUID and metadata of the parent collection.
\item Then the Bartender creates a new file entry within the Librarian with all the information we gave. 
\item The Librarian returns the GUID of this new entry.
\item Then the Bartender add the name \verb#proposal.pdf# and the new GUID to the collection \verb#/ourvo/common/docs# and from now on there will be a valid LN \verb#/ourvo/common/docs/proposal.pdf# which points to a file which has no replica at all. If someone tried to download the file called \verb#/ourvo/common/docs/proposal.pdf# now, would get an error message `try again later'.
\item The Bartender (using the information system) chooses a Shepherd and gets its endpoint reference. Then the Bartender initiates uploading of the file to the Shepherd: the request includes the size and checksum of the file, the GUID, and the protocols we are able to use.
\item The Shepherd creates a transfer URL and a referenceID for this file and registers the GUID of the file in its own database and reports to the Librarian that there is a new replica with state \verb#creating#. The Librarian gets the message from the Shepherd and creates a new entry in the locations list of the given file with the serviceID and the referenceID the Shepherd have just reported. If someone tries to download this file now, still gets a `try again later' error message, because this new replica is still not \verb#alive#.
\item The Shepherd returns the the TURL to the Bartender.
\item The Bartender returns the TURL to us.
\item Then we can upload the file to this TURL.
\item The Shepherd detects that the file is arrived and reports the change of state to \verb#alive# to the  Librarian who alters the state in the given file-entry. At this point the file has only one replica. 
\end{enumerate}
\begin{itemize}
\item The Shepherd periodically checks the Librarian if this is less than the needed replica number, and if it is then it initiates creating a new replica by a Bartender.
\item The Bartender chooses another Shepherd, initiates the transfer then returns the TURL to the  first Shepherd which uploads the file to the new Shepherd.
\item All the Shepherds check periodically whether their files have enough replica, and if any of them find that there is more replica needed, it initiates creating a new. If more than one Shepherd of course could cause that there will be more replicas than needed. If a Shepherd finds out that a file has more replicas than needed it notifies a Bartender about it.
\item The Bartender ask the Librarian about all Shepherds this file has replicas on, flags this file as `removing a replica' which prevents other Bartenders to remove an other replica accidentally, then make a decision of which one is to be removed, then contacts the chosen Shepherd and asks it to remove the replica. The Shepherd then notify the Librarian, and the Librarian removes the replica, and removes the flag `removing a replica' as well.
\item If we cannot upload the file to the given TURL for some reason, we could call \verb#addReplica# to get a new TURL without removing and recreating the file.
\end{itemize}

@@

>>>>

We have a file on our local disk we want to upload to a collection called \verb#/ourvo/common/docs#. (See Figure~\ref{fig:uploading}.)
\begin{enumerate}
\item We contact a Bartender to put the file, we give the size and checksum and other metadata, and the transfer protocols we want to use. And of course we give the Logical Name we want to be the name of the file, which in this case will be \verb#/ourvo/common/docs/proposal.pdf#
\item The Bartender ask a Librarian to traverse this LN.
\item If the Librarian can traverse the whole LN then this LN is already exists, but if the LN is still available and the parent exists, the Librarian’s response contains the GUID and metadata of the parent collection.
\item Then the Bartender creates a new file entry within the Librarian with all the information we gave. 
\item The Librarian returns the GUID of this new entry.
\item Then the Bartender add the name \verb#proposal.pdf# and the new GUID to the collection \verb#/ourvo/common/docs# and from now on there will be a valid LN \verb#/ourvo/common/docs/proposal.pdf# which points to a file which has no replica at all. If someone tried to download the file called \verb#/ourvo/common/docs/proposal.pdf# now, would get an error message `try again later'.
\item The Bartender (using the information system) chooses a Shepherd and gets its endpoint reference. Then the Bartender initiates uploading of the file to the Shepherd: the request includes the size and checksum of the file, the GUID, and the protocols we are able to use.
\item The Shepherd creates a transfer URL and a referenceID for this file and registers the GUID of the file in its own database and reports to the Librarian that there is a new replica with state \verb#creating#. The Librarian gets the message from the Shepherd and creates a new entry in the locations list of the given file with the serviceID and the referenceID the Shepherd have just reported. If someone tries to download this file now, still gets a `try again later' error message, because this new replica is still not \verb#alive#.
\item The Shepherd returns the the TURL to the Bartender.
\item The Bartender returns the TURL to us.
\item Then we can upload the file to this TURL.
\item The Shepherd detects that the file is arrived and reports the change of state to \verb#alive# to the  Librarian who alters the state in the given file-entry. At this point the file has only one replica. 
\end{enumerate}
\begin{itemize}
\item The Shepherd periodically checks the Librarian if this is less than the needed replica number, and if it is then it initiates creating a new replica by a Bartender.
\item The Bartender chooses another Shepherd, initiates the transfer then returns the TURL to the  first Shepherd which uploads the file to the new Shepherd.
\item All the Shepherds check periodically whether their files have enough replica, and if any of them find that there is more replica needed, it initiates creating a new. If more than one Shepherd of course could cause that there will be more replicas than needed. If a Shepherd finds out that a file has more replicas than needed it notifies a Bartender about it.
\item The Bartender ask the Librarian about all Shepherds this file has replicas on, flags this file as `removing a replica' which prevents other Bartenders to remove an other replica accidentally, then make a decision of which one is to be removed, then contacts the chosen Shepherd and asks it to remove the replica. The Shepherd then notify the Librarian, and the Librarian removes the replica, and removes the flag `removing a replica' as well.
\item If the client cannot upload the file to the given TURL for some reason, it is possible to call \verb#addReplica# to get a new TURL without removing and recreating the file.
\end{itemize}

@@

Some self-healing mechanisms are not implemented yet, e.g. the files and collections contains their parent-collections as their metadata, and of course a collection contains a list of its files and sub-collections, and if somehow this information became inconsistent, the system should detect and repair it. This is not implemented yet.
